### 2015-08-15 fundamentals/examples.tex
renames once through to No Recycle and 1-pass to Single-Pass Recycle and infinite-pass recycle to Inifinite-Pass Recycle

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference than new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the 1-pass recycle case are shown in Figure
\ref{fig:flowmodopen}.

@@

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a 1-pass
fuel cycle.  Note that because the reactors always transmute fuel into fixed
compositions, the error in isotopic compositions is larger for the
infinite-pass recycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
1-pass and infinite-pass cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
recycle scenario does not re-recycle material, it takes the fabrication
facility 2 cycles longer to accumulate a full batch of fissile material.

@@

Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
simulations of the once through, 1-pass recycle, and infinite-pass recycle
scenarios.  As the number of reactors (with staggered refueling) increases,
the behavior of the system approaches a more steady average reminiscent of
continuous material flow models.

>>>>

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference than new \gls{UOX} fuel. For the No Recycle case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the Infinite-Pass Recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

Cyclus' discrete materials make single-pass recycle straightforward to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead offers
it as a waste commodity which is only requested by the repository.  The
material flows for the Single-Pass Recycle case are shown in Figure
\ref{fig:flowmodopen}.

@@

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the No Recycle to a 1-pass
fuel cycle.  Note that because the reactors always transmute fuel into fixed
compositions, the error in isotopic compositions is larger for the
Infinite-Pass Recycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for No 
Recycle (once through), Single-Pass Recycle, and Infinite-Pass Recycle variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
1-pass and infinite-pass cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the Single-Pass Recycle case and every 9
cycles (180 months) for the Infinite-Pass Recycle case.  Because the 1-pass
recycle scenario does not re-recycle material, it takes the fabrication
facility 2 cycles longer to accumulate a full batch of fissile material.

@@

Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
simulations of the No Recycle, Single-Pass Recycle, and Infinite-Pass Recycle
scenarios.  As the number of reactors (with staggered refueling) increases,
the behavior of the system approaches a more steady average reminiscent of
continuous material flow models.
